Application-Level Regression Testing Framework using Jenkins

### 2017-04-12 manuscript/manuscript.tex
Added ORNL copyright notice, tweak acknowledment.

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
\documentclass{sig-alternate-05-2015}

@@

\graphicspath{{figures/}}
\pagestyle{plain}
\begin{document}

@@

\setcopyright{licensedusgovmixed}

@@

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}

@@

\graphicspath{{figures/}}
\pagestyle{plain}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\begin{document}

@@

@@

\blfootnote{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No. DE-AC05-00OR22725 with the U.S. Department of Energy. The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes. The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}

@@

% use section* for acknowledgement
\section*{Acknowledgment}
We thank Gary Rogers at NICS for his help in setting up and testing OTP integration. This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
